Data 621---HW1---Regression Model---Version 2

### 2020-09-09 HW1/RegModel_Adler.Rmd
Minor corrections

```{r trainStatTable}
knitr::kable(data.frame(Model = c("Null", "Saturated", "Stepwise Pairwise"),
                        Rsq = c(snm$r.squared, ssm$r.squared, sstm$r.squared),
                        AdjRsq = c(snm$adj.r.squared, ssm$adj.r.squared,
                                   ssm$adj.r.squared),
                        RMSE = c(sqrt(mean(nullModel$residuals ^ 2)),
                                 sqrt(mean(saturatedModel$residuals ^ 2)),
                                 sqrt(mean(stepModel$residuals ^ 2)))),
             digits = 3L, caption = 'Train Set Results')
```

#### Residual Plots
```{r residPlots, fig.height=7}
par(mfrow = c(2, 2))
plot(saturatedModel$fitted.values, studres(saturatedModel),
     main = 'Saturated Model', xlab = 'Predicted Values',
     ylab = 'Studentized Residuals', xlim = c(0, 160), ylim = c(-6, 6))
plot(stepModel$fitted.values, studres(stepModel),
     main = 'Stepwise Pairwise Model', xlab = 'Predicted Values',
     ylab = 'Studentized Residuals', xlim = c(0, 160), ylim = c(-6, 6))
plot(nullModel$fitted.values, studres(nullModel),
     main = 'Null Model', xlab = 'Predicted Values',
     ylab = 'Studentized Residuals', xlim = c(0, 160), ylim = c(-6, 6))
par(mfrow = c(1, 1))
```

@@

### Model Evaluations
In the table below are the RMSE and MAPE of each of the three models developed
above when applied to the **testing** set.

>>>>

```{r trainStatTable}
knitr::kable(data.frame(Model = c("Null", "Saturated", "Stepwise Pairwise"),
                        Rsq = c(snm$r.squared, ssm$r.squared, sstm$r.squared),
                        AdjRsq = c(snm$adj.r.squared, ssm$adj.r.squared,
                                   sstm$adj.r.squared),
                        RMSE = c(sqrt(mean(nullModel$residuals ^ 2)),
                                 sqrt(mean(saturatedModel$residuals ^ 2)),
                                 sqrt(mean(stepModel$residuals ^ 2)))),
             digits = 3L, caption = 'Train Set Results')
```

#### Residual Plots

```{r residPlots, fig.height=7}
par(mfrow = c(2, 2))
plot(saturatedModel$fitted.values, studres(saturatedModel),
     main = 'Saturated Model', xlab = 'Predicted Values',
     ylab = 'Studentized Residuals', xlim = c(0, 160), ylim = c(-6, 6))
plot(stepModel$fitted.values, studres(stepModel),
     main = 'Stepwise Pairwise Model', xlab = 'Predicted Values',
     ylab = 'Studentized Residuals', xlim = c(0, 160), ylim = c(-6, 6))
plot(nullModel$fitted.values, studres(nullModel),
     main = 'Null Model', xlab = 'Predicted Values',
     ylab = 'Studentized Residuals', xlim = c(0, 160), ylim = c(-6, 6))
par(mfrow = c(1, 1))
```

@@

### Model Evaluations
In the table below are the \(R^2\), adjusted \(R^2\), and RMSEfor each of the
three models developed above when applied to the **testing** set.
